The benefits of reporting critical effect size values

### 2024-08-22 paper/paper.Rmd
updating

In this section, we provide guidance and formulas for computing critical effect size values in general, with examples for frequently encountered effect sizes including Standardized Mean Differences (Cohen's $d$), correlations (Pearson's r), and raw and standardized coefficients in linear models. These formulas have been incorporated into R functions of the package "criticalESvalue" accessible at: https://github.com/psicostat/criticalESvalue, and are elaborated upon in the subsequent section.

>>>>

In this section, we provide guidance and formulas for computing critical effect size values in general, with examples for frequently encountered effect sizes including Standardized Mean Differences (Cohen's $d$), correlations (Pearson's r), and raw and standardized coefficients in linear models. These formulas have been incorporated into R functions of the package `criticalESvalue` accessible at: [https://github.com/psicostat/criticalESvalue](https://github.com/psicostat/criticalESvalue), and are elaborated upon in the subsequent section.

### 2024-08-22 paper/paper.tex
updating

In this section, we provide guidance and formulas for computing critical effect size values in general, with examples for frequently encountered effect sizes including Standardized Mean Differences (Cohen's \(d\)), correlations (Pearson's r), and raw and standardized coefficients in linear models. These formulas have been incorporated into R functions of the package ``criticalESvalue'' accessible at: \url{https://github.com/psicostat/criticalESvalue}, and are elaborated upon in the subsequent section.

>>>>

In this section, we provide guidance and formulas for computing critical effect size values in general, with examples for frequently encountered effect sizes including Standardized Mean Differences (Cohen's \(d\)), correlations (Pearson's r), and raw and standardized coefficients in linear models. These formulas have been incorporated into R functions of the package \texttt{criticalESvalue} accessible at: \url{https://github.com/psicostat/criticalESvalue}, and are elaborated upon in the subsequent section.
